Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-02 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

Starting from the top of the Table \@ref(tab:table), we see a statistically significant change
in home win percentage in 2020 from 2017-19, with p-value of 0.0365. The 95% 
confidence interval of (-0.255, -0.0075) confirms our belief that home-court 
advantage was lost in the 2020 NBA playoffs. However, after accounting for 
multiple tests using Bonferroni correction the p-value is no longer significant.
So, we may only cautiously say there is evidence that home-court advantage was 
not a factor in 2020.

@@

Away teams saw more of an impact than home teams. For starters, they saw a 
significant increase in mean points per game by about 5 points (95% CI: 2.083, 7.988)
Likewise, the away team two point shooting efficiency increased by an average of
about 0.03 (95% CI: 0.0147, 0.0503). However, unlike two point shooting, away 
teams did not see a statistically significant difference in three point and free
throw shooting. Overall, away teams have evidence of change in performance in 
the bubble. The away teams seemed to perform better than they would under normal
conditions as a visiting team.

>>>>

Starting from the top of the Table \@ref(tab:table), we see a statistically significant change
in home win percentage in 2020 from 2017-19, with p-value of 0.0365. The 95% 
confidence interval of (-0.255, -0.008) confirms our belief that home-court 
advantage was lost in the 2020 NBA playoffs. However, after accounting for 
multiple tests using Bonferroni correction the p-value is no longer significant.
So, we may only cautiously say there is evidence that home-court advantage was 
not a factor in 2020.

@@

Away teams saw more of an impact than home teams. For starters, they saw a 
significant increase in mean points per game by about 5 points (95% CI: 2.083, 7.988)
Likewise, the away team two point shooting efficiency increased by an average of
about 0.03 (95% CI: 0.015, 0.050). However, unlike two point shooting, away 
teams did not see a statistically significant difference in three point and free
throw shooting. Overall, away teams have evidence of change in performance in 
the bubble. The away teams seemed to perform better than they would under normal
conditions as a visiting team.
